% Amandeep Jutla - CV (pdfLaTeX)
% first version - 12/27/17

% based on latextemplates.com's modified version of Howard Wilson's template at
% https://github.com/watsonbox/cv_template_2004

% cc-by-nc-sa 3.0 

\documentclass[10pt]{article}

% Amandeep Jutla - CV structure/configuration/commands file
% 12/27/17

\usepackage{fourier} % utopia font
\usepackage[letterpaper, margin=1in]{geometry} 
\usepackage{fancyhdr} % Customize the header and footer
\usepackage{lastpage} % Required for calculating the number of pages in the document
\usepackage{color} % Required for custom colors
\usepackage{sectsty} % Allows customization of titles
\usepackage{titlesec} % must load before hyperref to avoid package conflict
\usepackage{hyperref} % Colors for links, text and headings

\setcounter{secnumdepth}{0} % Suppress section numbering

% set up header
\fancypagestyle{plain}{\fancyhf{}\cfoot{Jutla \thepage\ of \pageref{LastPage}}} % Define a custom page style
\pagestyle{plain} % Use the custom page style through the document
\renewcommand{\headrulewidth}{0pt} % Disable the default header rule
\renewcommand{\footrulewidth}{0pt} % Disable the default footer rule

\setlength\parindent{0pt} % Stop paragraph indentation
\setlength\parskip{3pt}

% Text width for tabbing environments
\newlength{\smallertextwidth}
\setlength{\smallertextwidth}{\textwidth}
\addtolength{\smallertextwidth}{-2cm}

% small caps for headings
\sectionfont{\color{black}} % Color section titles
\sectionfont{\scshape}

\titleformat{\subsection}[runin]
{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\renewcommand{\title}[1]{
{\huge{\color{black}\textbf{#1}}}\\ % Header section name and color
\rule{\textwidth}{0.5mm}\\ % Rule under the header
}

\newcommand{\training}[5]{
\begin{tabbing}
	\hspace{1cm} \= hspace{1cm} \= \kill
	{#1}--{#2} \> \> {#3}\\
	\> \> {#4}\\
	\> \> {#5}
\end{tabbing}
}

\newcommand{\award}[3]{
\begin{tabbing}
	\hspace{1cm} \= hspace{1cm} \= \kill
	{#1} \> \> {#2}\\
	\> \> {#3} 
\end{tabbing}
}

\newcommand{\leadership}[5]{
	\begin{tabbing}
		\hspace{1cm} \= hspace{1cm} \= \kill
		{#1}--{#2} \> \> {#3}\\
		\> \> {#4}\\
		\> \> {#5} 
	\end{tabbing}
}

\newcommand{\publication}[1]{\begin{flushleft}{#1}\end{flushleft}}
\newcommand{\teaching}[1]{\begin{flushleft}{#1}\end{flushleft}}
\newcommand{\lecture}[1]{\begin{flushleft}{#1}\end{flushleft}}

\begin{document}
\title{Amandeep Jutla}
\parbox[t][][t]{0.5\textwidth}{ % contact information block
\begin{tabbing} 
	\hspace{3cm} \= \hspace{4cm} \= \kill 
	{1051 Riverside Drive, Mail Unit 78}\\ 
	{New York, NY 10032}\\ 
	{(323) 347-1096}\\ 
	{\href{mailto:Amandeep.Jutla@nyspi.columbia.edu}{Amandeep.Jutla@nyspi.columbia.edu}}
\end{tabbing}}
\hfill % horizontal space between blocks
\parbox[t][][t]{0.5\textwidth}{ % "date prepared" block
\begin{tabbing} 
	\hspace{3cm} \= \hspace{4cm} \= \kill 
	{Date Prepared:} \> \today\\ 
\end{tabbing}}

\section{Education}

\begin{tabbing}
\hspace{1cm} \= hspace{1cm} \= hspace{1cm} \= \kill
{2012} \> \> M.D. \> University of Missouri, Kansas City School of Medicine\\[5pt]
{2008} \> \> B.A. \> University of Missouri, Kansas City
\end{tabbing}

\section{Post-Graduate Training}

\training
{2018}{}
{Postdoctoral Fellow}
{Whitaker Scholars in Developmental Neuropsychiatry Program}
{Columbia University}

\training
{2016}{2018}
{Child and Adolescent Psychiatry Fellow}
{Northwestern University Feinberg School of Medicine}
{Co-Chief Fellow, 2017--2018}

\training
{2012}{2016}
{Psychiatry Resident}
{University of California, Los Angeles San Fernando Valley}
{Chief Technology Resident, 2015--2016}

\section{Licensure and Certification}
\phantomsection
\subsection{State Licensure}

\begin{tabbing}
	\hspace{1cm} \= hspace{1cm} \= \kill
	{2018--2020} \> \> New York\\[5pt]
	{2016--2020} \> \> Illinois\\[5pt]
	{2014--2019} \> \> California
\end{tabbing}

\subsection{American Board of Psychiatry and Neurology Certification}

\begin{tabbing}
	\hspace{1cm} \= hspace{1cm} \= \kill
	{2018--2028} \> \> Child and Adolescent Psychiatry\\[5pt]
	{2016--2026} \> \> General Psychiatry
\end{tabbing}

\section{Honors and Awards}
\phantomsection
\subsection{National}

\award{2019}{Research Colloquium for Junior Investigators Award}{American Psychiatric Association}

\award{2018}{Systems of Care Clinical Poster Award}
{American Academy of Child and Adolescent Psychiatry}

\award{2017}{Outstanding Mentor Award}
{American Academy of Child and Adolescent Psychiatry}

\award{2017}{Educational Outreach Award}
{American Academy of Child and Adolescent Psychiatry}

\award{2016}{Educational Outreach Award}
{American Academy of Child and Adolescent Psychiatry}

\subsection{University}

\award{2019}{SHARP Machine Learning Scholarship Award for Early-Career Investigators}{Columbia University}

\award{2019}{Honorable Mention, Bender-Fishbein Award for Child Psychiatry Research}{Columbia University}

\award{2014}{Alex Rogawski Memorial Prize}
{University of California, Los Angeles Psychiatric Clinical Faculty Association}

\section{Professional Activities}
\phantomsection
\subsection{Society Membership}

\begin{tabbing}
	\hspace{1cm} \= hspace{1cm} \= \kill
	{2019--} \> \> International Society for Autism Research\\[5pt]
	{2018--} \> \> New York Academy of Sciences\\[5pt]
%	{2016--} \> \> National Physicians Alliance\\[5pt]
	{2014--} \> \> American Academy of Child and Adolescent Psychiatry\\[5pt]
	{2010--} \> \> American Psychiatric Association
\end{tabbing}

\subsection{Leadership and Committee Involvement}

\leadership{2018--}{}{Career Development Working Group}{Autism and Intellectual Disability Committee}{American Academy of Child and Adolescent Psychiatry}

\leadership{2015}{2016}{Resident/Fellow Representative}{Southern California Psychiatric Society}{}

\subsection{Peer Review Activities}

\begin{flushleft}\textit{Journal of Autism and Developmental Disorders} (2)\\
\textit{Autism Research} (3)\end{flushleft}%\\[5pt]

\section{Publications}
\phantomsection
\subsection{Peer-Reviewed Papers}

\publication{\textbf{Jutla A}, Turner JB, Snyder LG, Chung WK, Veenstra-VanderWeele J. ``Psychotic symptoms in 16p11.2 copy number variant carriers.'' Manuscript under review. Preprint in \textit{bioRxiv}: May 2019:621250. {\href{https://www.biorxiv.org/content/10.1101/621250v1}{doi:10.1101/621250}}.}

\subsection{Editorials}

\publication{\textbf{Jutla A},  Reed H, Veenstra-VanderWeele J. ``The architecture of autism spectrum disorder risk: what do we know, and where do we go from here?'' \textit{JAMA Psychiatry}. July 2019. {\href{https://doi.org/10.1001/jamapsychiatry.2019.1375}{doi:10.1001/jamapsychiatry.2019.1375}}.}

% \publication{\textbf{Jutla A}. ``Reconstructing depression.'' \textit{Journal of the Psychiatric Clinical Faculty Association}. 2014; (Fall): {\href{https://doi.org/10.13140/RG.2.2.10268.54406}{doi:10.13140/RG.2.2.10268.54406}}.}

\subsection{Chapters}

\publication{Johnson MR, Hatzis NM, \textbf{Jutla A}. ``Children and adolescents.'' In: Roberts LW, ed. \textit{The American Psychiatric Association Publishing Textbook of Psychiatry.} 7\textsuperscript{th} ed. Washington, DC: American Psychiatric Association Publishing; 2019.}

\publication{Plioplys S, \textbf{Jutla A}. ``Psychogenic non-epileptic seizures and comorbid epilepsy in an adolescent.'' In: Hauptman AJ, Salpekar JA, eds. \textit{Pediatric Neuropsychiatry: A Case-Based Approach.} Cham, Switzerland: Springer; 2019:167-178. {\href{https://doi.org/10.1007/978-3-319-94998-7_16}{doi:10.1007/978-3-319-94998-7\_16}}}

\publication{\textbf{Jutla A}. ``Romance, relationships, and residency.'' In: Foreman T, Dickstein LJ, Garakani A, Jordan A, Richards M, eds. \textit{A Resident's Guide to Surviving Psychiatric Training}. 3\textsuperscript{rd} ed. Arlington, VA: American Psychiatric Association; 2016:184-186.}

\publication{\textbf{Jutla A}. ``Subspecialty training in psychiatry.'' In: Foreman T, Dickstein LJ, Garakani A, Jordan A, Richards M, eds. \textit{A Resident's Guide to Surviving Psychiatric Training}. 3\textsuperscript{rd} ed. Arlington, VA: American Psychiatric Association; 2016:190-195.}

\section{Presentations}

\subsection{Conference Presentations} (* denotes presenting author)

\publication{\textbf{Jutla A*}, Foss-Feig J, Donohue MR, Veenstra-VanderWeele J. ``The relationship between autism spectrum disorder and prodromal psychosis in the Adolescent Brain Cognitive Development cohort.'' Oral presentation and poster to be given at: American College of Neuropsychopharmacology, 58\textsuperscript{th} Annual Meeting; December 8 \& 9, 2019; Orlando, FL.}

\publication{\textbf{Jutla A}. ``Psychosis in autism spectrum disorder.'' Oral presentation to be given at: American Academy of Child and Adolescent Psychiatry, 66\textsuperscript{th} Annual Meeting; Clinical Perspectives: Complex Presentations of Autism Spectrum Disorder: Beyond the Core Features; October 18, 2019; Chicago, IL.}

\publication{\textbf{Jutla A}. ``16p11.2 duplication as a model of psychosis in autism spectrum disorder.'' Oral presentation and poster at: American Psychiatric Association, 2019 Annual Meeting; Research Colloquium for Junior Investigators; May 19, 2019; San Francisco, CA. {\href{https://doi.org/10.13140/RG.2.2.11464.57602}{doi:10.13140/RG.2.2.11464.57602}}.}

\publication{\textbf{Jutla A*}, Chung WK, Veenstra-VanderWeele J. ``Predictors of psychotic symptoms among 16p11.2 copy number variant carriers.'' Poster at: International Society for Autism Research, 2019 Annual Meeting; May 2, 2019; Montreal, Canada. {\href{https://doi.org/10.13140/RG.2.2.35791.53922}{doi:10.13140/RG.2.2.35791.53922}}.}

\publication{\textbf{Jutla A}. ``Prevalence and correlates of attention-deficit/hyperactivity disorder among youth with 16p11.2 copy number variation.'' Oral presentation and poster at: American Professional Society of ADHD and Related Disorders, 2019 Annual Meeting; January 19, 2019; Washington, DC. {\href{https://doi.org/10.13140/RG.2.2.27091.41444}{doi.org/10.13140/RG.2.2.27091.41444}}.}

\publication{Lee E*, \textbf{Jutla A}. ``Obsessive-compulsive disorder presenting with catatonia: a case report and systematic review of the literature.'' Poster at: American Academy of Child and Adolescent Psychiatry, 65\textsuperscript{th} Annual Meeting; October 25, 2018; Seattle, WA. {\href{https://doi.org/10.1016/j.jaac.2018.09.255}{doi:10.1016/j.jaac.2018.09.255}}.}

\publication{\textbf{Jutla A*}, Wang L, Lavigne J, Yang S, Csernansky J. ``Resting-state connectivity in adolescents with psychogenic non-epileptic seizures.'' Oral presentation at: American Academy of Child and Adolescent Psychiatry, 65\textsuperscript{th} Annual Meeting; Symposium: Conversion and Anxiety: New Neuroimaging Evidence and Clinical Correlates; October 24, 2018; Seattle, WA. {\href{https://doi.org/10.1016/j.jaac.2018.07.676
}{doi:10.1016/j.jaac.2018.07.676}}.}

\publication{Ahmed A, \textbf{Jutla A*}. ``Can psychosis-associated creatine kinase-emia be a marker of underlying disease? A case report and review of the literature.'' Poster at: American Academy of Child and Adolescent Psychiatry, 65\textsuperscript{th} Annual Meeting; October 24, 2018; Seattle, WA. {\href{https://doi.org/10.1016/j.jaac.2018.09.108}{doi:10.1016/j.jaac.2018.09.108}}.}

\publication{\textbf{Jutla A}. ``Barriers to optimal psychiatric care for adolescents with co-occurring developmental disability and severe mental illness in New York State.'' Poster at: American Academy of Child and Adolescent Psychiatry, 65\textsuperscript{th} Annual Meeting; Systems of Care Special Program: Improving Care for Youth with ASD and Intellectual Disabilities; October 22, 2018; Seattle, WA. {\href{https://doi.org/10.13140/RG.2.2.15281.43363}{doi:10.13140/RG.2.2.15281.43363}}.}

\publication{\textbf{Jutla A*}, Smith AM, Folmsbee SS. ``Complexities in the neurodevelopmental presentation and psychiatric management of a child with multiple inherited chromosomal abnormalities.'' Poster at: American Psychiatric Association, 2018 Annual Meeting; May 6, 2018; New York, NY. {\href{https://doi.org/10.13140/RG.2.2.19698.81608}{doi:10.13140/RG.2.2.19698.81608}}.}

\publication{Moreno AM*, \textbf{Jutla A}, Weiss AG, MacKenzie JM. ``Effectiveness of undergraduate and graduate medical education in preparing pediatricians to manage psychiatric problems.'' Poster at: American Academy of Child and Adolescent Psychiatry, 64\textsuperscript{th} Annual Meeting; October 25, 2017; Washington, DC. {\href{https://doi.org/10.1016/j.jaac.2017.09.084}{ doi:10.1016/j.jaac.2017.09.084}}.}

\publication{\textbf{Jutla A}. ``Prenatal antidepressant exposure as a risk factor for autism spectrum disorder: an examination of the evidence.'' Poster at: American Academy of Child and Adolescent Psychiatry, 63\textsuperscript{rd} Annual Meeting; October 26, 2016; New York, NY. {\href{https://doi.org/10.1016/j.jaac.2016.09.016}{ doi:10.1016/j.jaac.2016.09.016}}.}

\publication{\textbf{Jutla A*}, Ramos N. ``An `atypical' case of neuroleptic malignant syndrome.'' Poster at: American Academy of Child and Adolescent Psychiatry, 62\textsuperscript{nd} Annual Meeting; October 23, 2015; San Antonio, TX. {\href{https://doi.org/10.13140/RG.2.2.33120.58888}{doi:10.13140/RG.2.2.33120.58888}}.}

\subsection{Talks}

\lecture{Tioleco N, \textbf{Jutla A}, Reed HE, Whitaker AH. ``\textit{Life, Animated}: How Disney movies helped a boy with ASD connect.'' To be presented at: American Academy of Child and Adolescent Psychiatry, 66\textsuperscript{th} Annual Meeting; Media Theatre: \textit{Life, Animated}; October 15, 2019; Chicago, IL.}

\lecture{\textbf{Jutla A}, Walkup JT. ``Conceptualization of an adolescent with untreated anxiety of childhood.'' Presented at: Northwestern University Feinberg School of Medicine, Psychiatry Grand Rounds; February 14, 2018; Chicago, IL.}

\lecture{\textbf{Jutla A}, Lavigne JV. ``Killing yourself to live: unpacking the paradox of cancer treatment.'' Presented at: Ann \& Robert H. Lurie Children's Hospital, Department of Child and Adolescent Psychiatry, Multidisciplinary Case Conference; September 11, 2017; Chicago, IL.}

\lecture{Ahmed A, \textbf{Jutla A}. ``ADHD and related syndromes: an overview.'' Presented at: Chicago Public Schools Clinical Staff Professional Development Seminar; August 30, 2017; Chicago, IL.}

\lecture{\textbf{Jutla A}, MacKenzie JM. ``Making decisions about suicide risk: three cases, three judgments.'' Presented at: Ann \& Robert H. Lurie Children's Hospital, Department of Child and Adolescent Psychiatry, Multidisciplinary Case Conference; November 14, 2016; Chicago, IL.}

\lecture{\textbf{Jutla A}, MacKenzie JM. ``An approach to the conceptualization and assessment of conversion disorder.'' Presented at: 21\textsuperscript{st} Annual Midwest Conference of Child Life Specialists; November 6, 2016; Chicago, IL.}

\lecture{\textbf{Jutla A}, MacKenzie JM. ``Pediatric conversion disorder: a consultation service perspective.'' Presented at: Loyola University Stritch School of Medicine, Psychiatry Grand Rounds; September 1, 2016; Maywood, IL.}

\lecture{\textbf{Jutla A}. ``Future directions in antidepressant pharmacotherapy.'' Presented at: VA Greater Los Angeles Healthcare System, Sepulveda Ambulatory Care Center, Psychiatry Grand Rounds; February 12, 2014; North Hills, CA.}

\section{Teaching}

\begin{tabbing}
	\hspace{1cm} \= hspace{1cm} \= hspace{1cm} \= \kill
	{7/29/19--8/4/19} \> \> Teaching assistant\\
					  \> \> Workshop on Autism Spectrum Disorders\\
					  \> \> Cold Spring Harbor Laboratory\\[5pt]

	{4/10/19}		  \> \> Discussant, ``Child development''\\
					  \> \> Board Review Seminar Series\\
					  \> \> Columbia/Cornell/NewYork-Presbyterian Hospital Child Psychiatry Fellowship\\[5pt]

	{3/13/19}		\> \> Lecturer, \> ``Pharmacologic treatment of co-occurring psychiatric symptoms in youth\\
					\> \> \>  \hphantom{ } with autism spectrum disorder''\\ 
					\> \> Management of Aggression in Youth with Autism Spectrum Disorder Theme Day\\ 
					\> \> Columbia/Cornell/NewYork-Presbyterian Hospital Child Psychiatry Fellowship\\[5pt]

	{2/27/19}		  \> \> Discussant, ``Intellectual disability and developmental disorders''\\
					  \> \> Board Review Seminar Series\\
					  \> \> Columbia/Cornell/NewYork-Presbyterian Hospital Child Psychiatry Fellowship\\[5pt]

	{2017--2018}	\> \> Lecturer, ``Overview of child psychiatry''\\
					\> \> Psychiatry Clerkship Lecture Series\\
					\> \> Northwestern University Feinberg School of Medicine\\
					\> \> Dates: \> 6/5/18, 4/24/18, 2/27/18, 1/30/18, 12/5/17, 11/7/17, 10/10/17, 9/19/17,\\ 
					\> \> \> 		8/8/17, 7/18/17, 6/20/17, 5/16/17, 4/18/17, 3/21/17, 2/21/17.\\[5pt]

	{2018, 2016}	\> \> Lecturer, ``Emotional and behavioral problems in children and adolescents''\\
					\> \> Northwestern University Pediatric Otolaryngology Fellowship\\
					\> \> Columbia/Cornell/NewYork-Presbyterian Hospital Child Psychiatry Fellowship\\
					\> \> Dates: \> 4/4/18, 11/30/16.\\[5pt]


	{9/27/17}		\> \> Lecturer, ``Child psychiatry for pediatricians''\\
					\> \> Northwestern University Pediatrics Residency\\[5pt]
	
	{2017}			\> \> Workshop leader\\
					\> \> Medical Decision-Making\\
					\> \> Northwestern University Feinberg School of Medicine\\
					\> \> Dates: \> 2/9/17, 2/22/17, 3/9/17, 3/22/17, 4/20/17.\end{tabbing}

					\end{document}
