% Amandeep Jutla - CV (pdfLaTeX)
% first version - 12/27/17

% based on latextemplates.com's modified version of Howard Wilson's template at
% https://github.com/watsonbox/cv_template_2004

% cc-by-nc-sa 3.0 

\documentclass[10pt]{article}

\input{structure.tex}

\begin{document}
\title{Amandeep Jutla}
\parbox[t][][t]{0.5\textwidth}{ % contact information block
\begin{tabbing} 
	\hspace{3cm} \= \hspace{4cm} \= \kill 
	{225 E Chicago Ave, Box 10}\\ 
	{Chicago, IL 60611}\\ 
	{(312) 227-3420}\\ 
	{\href{mailto:ajutla@northwestern.edu}{ajutla@northwestern.edu}}
\end{tabbing}}
\hfill % horizontal space between blocks
\parbox[t][][t]{0.5\textwidth}{ % "date prepared" block
\begin{tabbing} 
	\hspace{3cm} \= \hspace{4cm} \= \kill 
	{Date Prepared:} \> \today\\ 
\end{tabbing}}

\section{Personal Data}
\begin{tabbing}
\hspace{3cm} \= \kill
{Name} \> Amandeep Jutla\\
{Date of Birth} \> October 6\textsuperscript{th}, 1988\\
{Birthplace} \> Manhattan, Kansas\\
{Citizenship} \> U.S.
\end{tabbing}

\section{Training}
\training
{7/2016}{6/2018}
{Child and Adolescent Psychiatry Fellow}
{Department of Psychiatry and Behavioral Sciences}
{Northwestern University}
{Co-Chief Fellow, 2017--2018}

\training
{7/2012}{6/2016}
{Psychiatry Resident}
{Department of Psychiatry and Biobehavioral Sciences}
{University of California, Los Angeles (San Fernando Valley Program)}
{Chief Technology Resident, 2015--2016}

\section{Education}

\begin{tabbing}
	\hspace{3cm} \= hspace{1cm} \= \kill
	{2012} \> M.D. \> University of Missouri, Kansas City School of Medicine\\[5pt]
	{2008} \> B.A. \> University of Missouri, Kansas City
\end{tabbing}

\section{Licensure and Board Certification}

\subsection{State Licensure}

\begin{tabbing}
	\hspace{3cm} \= \kill
	{2016--Present} \> Illinois\\[5pt]
	{2014--Present} \> California
\end{tabbing}

\subsection{American Board of Psychiatry and Neurology Certification}

\begin{tabbing}
	\hspace{3cm} \= \kill
	{2018 (anticipated)} \> Child and Adolescent Psychiatry\\[5pt]
	{2016--Present} \> General Psychiatry
\end{tabbing}

\section{Honors}

\subsection{National}

\award{2017}{Outstanding Mentor Award}
{American Academy of Child and Adolescent Psychiatry}

\award{2017}{Educational Outreach Award}
{American Academy of Child and Adolescent Psychiatry}

\award{2016}{Educational Outreach Award}
{American Academy of Child and Adolescent Psychiatry}

\subsection{University}

% award with added description
\begin{tabbing}
	\hspace{3cm} \= \kill
	{2014} \> {Alex Rogawski Memorial Prize}\\
	\> {UCLA Clinical Faculty Association}\\
	\> {\$2,500 prize for ``best original paper relating to psychiatric theory'' by a UCLA trainee}
\end{tabbing}

\section{Professional Organizations, Societies and Service}

\subsection{National Memberships and Positions}

\begin{tabbing}
	\hspace{3cm} \= \kill
	{2016--Present} \> National Physicians Alliance\\[5pt]
	{2014--Present} \> American Academy of Child and Adolescent Psychiatry\\[5pt]
	{2010--Present} \> American Psychiatric Association
\end{tabbing}

\subsection{Regional Memberships and Positions}

\begin{tabbing}
	\hspace{3cm} \= \kill
	{2016--Present} \> Illinois Council of Child and Adolescent Psychiatry\\[5pt]
	{2016--Present} \> Illinois Psychiatric Society
\end{tabbing}

\subsection{Leadership}

\leadership{2015}{2016}{Resident/Fellow Representative}{Southern California Psychiatric Society}

\section{Teaching Experience and Responsibilities}

\subsection{Specific Courses (Northwestern University Feinberg School of Medicine)}

\teaching{Psychiatry Clerkship Lecture Series (``Overview of child psychiatry'' lecture for rotating third-year medical students, given monthly from March 2017 to present)}

\teaching{Pediatrics Resident Didactics (``Child psychiatry for pediatricians'', October 2017)}

\teaching{Medical Decision-Making (workshop leader for first-year medical students, Spring 2017)}

\teaching{Otolaryngology Resident and Fellow Didactics (``Treatment considerations for agitation in pediatric presentations'', November 2016; ``Emotional and behavioral problems in children and adolescents'', April 2018)}

\subsection{Specific Courses (David Geffen School of Medicine at UCLA)}

\teaching{Introduction to Psychiatry Course (``Psychiatric diagnosis,'' ``Antidepressants'' and ``Antipsychotics'' lectures for rotating third-year medical students at Olive View--UCLA Medical Center; given twice monthly from July 2015 to June 2016)}

\section{Publications}

\subsection{Books and Chapters}

\publication{Plioplys S, \textbf{Jutla A}. ``Psychogenic non-epileptic seizures and comorbid epilepsy in an adolescent.'' In: Hauptman AJ, Salpekar JA, eds. \textit{Pediatric Neuropsychiatry: A Clinical Casebook.} Cham, Switzerland: Springer. In press.}

\publication{Johnson MR, Hatzis NM, \textbf{Jutla A}. ``Treatment of children and adolescents.'' In: Roberts LW, Hales R, eds. \textit{The American Psychiatric Association Publishing Textbook of Psychiatry.} 7th ed. Arlington, VA: APA Publishing. In press.}

\publication{\textbf{Jutla A}. ``Romance, relationships, and residency.'' In: Foreman T, Dickstein LJ, Garakani A, Jordan A, Richards M, eds. \textit{A Resident's Guide to Surviving Psychiatric Training}. 3rd ed. Arlington, VA: APA Publishing; 2016:184-186.}

\publication{\textbf{Jutla A}. ``Subspecialty training in psychiatry.'' In: Foreman T, Dickstein LJ, Garakani A, Jordan A, Richards M, eds. \textit{A Resident's Guide to Surviving Psychiatric Training}. 3rd ed. Arlington, VA: APA Publishing; 2016:190-195.}

\subsection{Reviews and Editorials}

\publication{\textbf{Jutla A}. ``Reconstructing depression.'' \textit{Journal of the Psychiatric Clinical Faculty Association}. 2014; (Fall): {\href{https://www.semel.ucla.edu/pcfa/articles}{https://www.semel.ucla.edu/pcfa/articles}}.}

\subsection{Abstracts} (* denotes presenting author)

\publication{\textbf{Jutla A*}, Smith AM, Folmsbee SS. ``Complexities in the neurodevelopmental presentation and psychiatric management of a child with multiple inherited chromosomal abnormalities.'' Presented at: American Psychiatric Association, 2018 Annual Meeting; May 6, 2018; New York, NY. doi:10.13140/RG.2.2.19698.81608.}

\publication{Moreno AM*, \textbf{Jutla A}, Weiss AG, MacKenzie JM. ``Effectiveness of undergraduate and graduate medical education in preparing pediatricians to manage psychiatric problems.'' Presented at: American Academy of Child and Adolescent Psychiatry, 64th Annual Meeting; October 25, 2017; Washington, DC. doi:10.1016/j.jaac.2017.09.084.}

\publication{\textbf{Jutla A*}. ``Prenatal antidepressant exposure as a risk factor for autism spectrum disorder: an examination of the evidence.'' Presented at: American Academy of Child and Adolescent Psychiatry, 63rd Annual Meeting; October 26, 2016; New York, NY. doi:10.1016/j.jaac.2016.09.016.}

\publication{\textbf{Jutla A*}, Ramos N. ``An `atypical' case of neuroleptic malignant syndrome.'' Presented at: American Academy of Child and Adolescent Psychiatry, 62nd Annual Meeting; October 23, 2015; San Antonio, TX. doi:10.13140/RG.2.2.33120.58888.}

\end{document}